\documentclass[11pt]{article}
\oddsidemargin 0in
\evensidemargin 0in
\topmargin -1in
\textwidth 6.5in
\textheight 9in
\parindent 0in

\begin{document}

\begin{center}
{\bf\Large Foreward}
\end{center}

\noindent

This volume contains the papers presented at the tenth annual ACM
Workshop on Digital Rights Management (DRM), sponsored by the ACM
SIGSAC and held in conjunction with the 17th ACM Conference on
Computer Computer and Communications Security (CSS).  The daylong
workshop consisted of  informal discussions, invited talks and
peer-reviewed technical talks describing recent research
contributions, including relatively mature work (regular papers) and
more preliminary
work-in-progress work (short papers). ~\\

As in the past, the workshop provided an international forum that
serves as an interdisciplinary bridge between areas that can be
applied to DRM, including: cryptography, software, systems
architecture and framework design, policy-management as well as
various application areas including medical data management and
securing program control flows. In addition, this year we were
privileged to have two invited talks from different cross-sections
of the DRM realm. The first of these was provided by Moni Naor, a
very well-known professor on cryptography at Weizmann Institute of
Science. The second invited talk was given by Warren Lieberfarb, an
industry visionary on digital media and
the former President of Warner Home Video (WHV).~\\

We would like to thank all of the authors who submitted papers to
this year's workshop, the invited speakers, as well as the program
committee members and external reviewers who participated in the
review process.   In addition, we are grateful for the support of
the ACM SIGSAC, Microsoft and Technicolor for hosting and sponsoring
the workshop.  Finally, we acknowledge the hard work of Lisa M.
Tolles at Sheridan Printing, who produced this proceedings volume.
~\\

\begin{tabbing}
{\it ACM-DRM'10}  \ \ \ \ \ \ \ \ \ \ \ \= {\bf Hongxia Jin} \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \ \= {\bf Marc Joye} \\
{\it Proceedings Editors} \> IBM Research at Almaden \>  Technicolor, France\\
{\it co-Program Chairs}
\end{tabbing}
\end{document}
